A Graph Theoretic Approach to Problem Formulation for Multidisciplinary Design Analysis and Optimization

### 2013-08-07 conclusions.tex
files for submitted version and reviewer 3's comments

\section*{Conclusions}
In this paper, we have presented an approach for describing  MDAO problems with 
with a graph based syntax.  Our graph description shares 
similarities to other approaches such as REMS, FDT, DSM, and XDSM, but 
it provides new constructs tailored to applications in early phases of the design 
process where a problem formulation has not yet been fully formed.   
In particular, we introduce the concepts of the Maximal Connectivity Graph (MCG) 
and the Fundamental Problem Graph (FPG).

The MCG addresses the question, ``Given a set of analysis tools and design objectives, what are all 
of the potential problem formulations that could exist to solve a design problem?''  
The MCG provides a structured formalism to reduce the, potentially very large, 
set of valid combinations of analysis tools to a single subset and to identify
conflicts that could prevent a valid problem formulation.
Conflicts can originate from two sources: holes and collisisons. A hole 
corresponds to a variable that is not calculated by any analysis block in the 
MCG but is needed by other blocks. To create a valid problem formulation, all 
holes must be ``filled'' either by selecting the corresponding variable as a 
design variable, or by introducing additional analysis tools to compute the variable.  
A collision happens when two or more analysis tools compute values for the same variable.  
To create a valid problem formulation, all collisions must be resolved either by 
removing redundant analysis tools or by explicitly allowing the redundencies to remain 
in the form of a multifidelity problem. For the latter case, a special solution 
method will need to be employed to manage the multifidelity situation and decide 
when to execute the different analysis tools. Resolving collisions and filling 
holes in an MCG both require choices by the designer to shape the overall
MDAO problem to meet the needs of the problem he/she is trying to solve.

The FPG represents the problem as an engineer would describe it: ``Given a specific set of tools, 
with a set of design vairables, find design that best meets a given objective
within the given constraints.'' Although an FPG uniquely defines a single MDAO problem, 
there is not necessarily a unique FPG for any given MCG. In Section 
\ref{s:building graphs} we provide an algorithm 
that reduces an MCG, via the resolution of conflicts in the graph, down to an FPG. 
How one goes about resolving the conflicts will determine which particular FPG is reached. 
One benefit of using graph theory is the standard techniques, such as cycle 
detection, which can be used to inform the user's decisions and make the process of conflict 
resolution much easier.

In Section \ref{s:example problem}, we provide an example of 
formulating different FPGs from an MCG for a commercial aircraft design problem. This problem includes 8 
analysis tools and approximately 20 variables. Despite this relatively modest size, 
the MCG is rich enough to provide for a number of different valid FPGs. This demonstrates
the inherant value of the MCG to the design process by providing a mechanism for selecting 
an FPG based on important factors such as available design cycle time, consideration of 
coupling effects, or desired fidelity. Even after downselecting to a single FPG, the 
MCG itself still remains a useful tool. No real design problem is static, and will always
evolve throughout the design process. New tools may be introduced to account for previously 
unexpected effects and new constraints or objectives can be introduced. When this occurs, 
the MCG provides the opportunity to account for these changes by starting over with the 
algorithm from Section \ref{s:building graphs} to downselect to the most effective new FPG. 
While it is possible that this new FPG will be very similar to the previous one, 
it is also very possible that it will be different in significant ways. 
By repeating downselection algorithm from the MCG you allow for any new interdisciplinary couplings and  
information conflicts to play a role in selecting the most appropriate FPG.

Once a desired FPG is identified, the graph syntax described in the paper can be 
leveraged to formulate a Problem Solution Graph (PSG). This graph includes all of the 
same information from the FPG while additionally describing the particular MDAO 
solution architecture, e.g. MDF, IDF, BLISS, ATC, that will be used to solve the problem.  
Many possible PSGs could be formulated to solve a problem corresponding to a 
specified FPG. The application of the syntax to PSGs has not been illustrated in the paper, 
but the basic concept of applying multiple solution strategies to a given problem 
formulation has been well established by a number of MDAO architecture 
benchmarking efforts\cite{Tedford2009,gray2013}. Furthermore the validity of applying 
graph syntax to the description of specific problem solutions has been demonstrated 
by XDSM.

>>>>

\section*{Conclusions}
In this paper, we have presented an approach for describing MDAO problems with constructs and syntax from graph theory. 
Our graph description shares similarities to other approaches such as REMS, $\Psi$, FDT, DSM, and XDSM, but it provides new constructs tailored to applications in early phases of MDAO problem formulation before specific problem solution approaches are envisioned. 
In particular, we introduce the concepts of the Maximally Connected Graph (MCG) and the Fundamental Problem Graph (FPG).

The MCG addresses the question, ``Given a set of analysis tools, what are all of the variable interconnections between them that could be established?''  
The MCG provides a structured formalism to identify \textit{holes} and \textit{collisions} in interconnections between input and output variables implied by the set of analysis tools. 
A hole corresponds to a variable that is not calculated in the MCG data flow but is needed by other tools. 
To create a valid problem formulation, all holes must be ``filled'' either by assigning the corresponding variable as a design variable to be set by the user or an optimizer, or by introducing additional tools to compute the variable.

A collision corresponds to a situation in which two or more analysis tools compute separate instances of the same variable. 
To create a valid problem formulation, all collisions must be resolved either by removing redundant analysis tools or by introducing logic or solvers into the data flow to choose between or aggregate multiple instances during execution. 
The identification of collisions in an MCG is especially important for problem formulations involving multiples analysis tools of different fidelities; in this context, a collision represents an opportunity to formulate a multi-fidelity problem that can take best advantage of the efficiency/accuracy tradeoff between different analysis tools. 
Resolving collisions and filling holes in an MCG requires choices by the user to specify the overall MDAO problem that he/she desires to solve, i.e. to produce the required set of system-level outputs given a specified set of design variables. 
One benefit of a graph theoretic approach is the standard algorithms which can be used to inform the user's decisions, such as cycle detection, minimum spanning trees, and shortest path algorithms.

The FPG is a graph that describes a data connection structure corresponding to an MDAO problem formulation free of collisions and holes. 
An FPG is the result of user choices to fill holes and resolve collisions in the initial MCG. 
Typically, many different FPGs could be attained from a given MCG, depending on the user choices. 
The number of possible FPGs that can be attained by selecting different design variables or introducing additional analysis tools to fill holes and/or resolve collisions can be viewed as a measure of the freedom available to the user in implementing the available analysis tools to formulate valid MDAO problems. 
In Sec.~\ref{s:building graphs}, we present an algorithm for identifying holes and conflicts in an MCG that can be applied by the user in a process to arrive at valid FPGs. 
In Sec.~\ref{s:example problem}, we provide an example application of formulating an FPG from an MCG for a commercial aircraft design problem.

Once a desired FPG is identified, the graph syntax described in the paper can be leveraged to formulate a Problem Solution Graph (PSG). The PSG describes particular MDAO solution architectures, e.g. MDF, IDF, BLISS, ATC, that can be used to solve the problem defined by the FPG. 
Many possible PSGs could be formulated to solve a problem corresponding to a specified FPG.  
The application of the syntax to PSGs has not been illustrated in the paper.

### 2013-08-07 example_problem.tex
files for submitted version and reviewer 3's comments

\section{Example Problem}
	\label{s:example problem}
	This section presents an example problem to demonstrate the process of obtaining the FPG and the advantages of doing so. 
The example task is to create an FPG for the conceptual sizing of a single-aisle subsonic transport using a set of analysis tools with objectives including performance and gross weight for a required mission. 
	The full set of analysis codes available for use is provided in Table \ref{t:analysis codes}.
	\begin{table}[htbp]
	  \centering
	  \caption{Analysis codes for subsonic transport sizing}
		\begin{tabular}{cc}
		\toprule
		analysis code & description \\
		\midrule
		VSP   & parametric vehicle geometry \\
		PDCYL & wing and fuselage weight estimation \\
		NPSS  & engine sizing and performance \\
		VORLAX & aerodynamics using the vortex lattice method \\
		PMARC & aerodynamics using a low-order panel method \\
		WATE  & engine weight estimation \\
		FLOPSa & mission performance, \\
		  & engine sizing, and weight estimation \\
		FLOPSb & mission performance only \\
		\bottomrule
		\end{tabular}%
	  \label{t:analysis codes}%
	\end{table}%
	Each analysis code contributes individual disciplinary analysis capability, but the outputs of the codes are not mutually exclusive. 
	For example, VORLAX and PMARC are both aerodynamics codes that predict inviscid drag but with different levels of fidelity. 
	The Flight Optimization System (FLOPS) is included twice to represent two different configurations corresponding to different uses. 
	FLOPSa denotes FLOPS implemented to execute both mission performance and engine analysis, while FLOPSb indicates  FLOPS implemented to execute for only mission performance analysis. 
	This representation is useful for ``supercodes'' that are capable of being implemented in different ways and with different sets of inputs and outputs.
The enumeration of these analysis tools and objectives concludes step (A) in Sec.~\ref{ss:process}.

Step (B) is the production of the MCG.
	In this example, the MCG is formed using a consistant variable naming convention and then connecting all variables with the same name with connection edges. 
	Table \ref{t:ins and outs} presents the full list of variables in the leftmost column and indicates whether the variable is an input or an output of each analysis code. 
	Some variables, such as geometry and performance, represent groups of variables that are passed as arrays or other data structures due to their similarity. 
	This bundling of variables is not fundamental and does not limit the generality of this example; rather, it simplifies the presentation.
	\begin{table}[htb!]
	  \centering
	  \caption{Analysis code input and output description}
		\begin{tabular}{ccccccccc}
		\toprule
		variable & \multicolumn{8}{c}{analysis code} \\
		\midrule
			  & VSP   & PDCYL & NPSS  & VORLAX & PMARC & WATE  & FLOPSa & FLOPSb \\
		geometry & in    & in    &       & in    & in    & in    & in    & in \\
		number of engines &       &       & in    &       &       &       & in    & in \\
		mission &       &       &       &       &       &       & in    & in \\
		fuselage weight &       & out   &       &       &       &       & in    & in \\
		wing weight &       & out   &       &       &       &       & in    & in \\
		engine weight &       &       &       &       &       & out   & out   & in \\
		wetted area & out   &       &       &       &       &       & in    & in \\
		inviscid drag &       &       &       & out   & out   &       &       & in \\
		drag  &       &       & in    &       &       &       & out   & out \\
		engine performance &       &       & out   &       &       & in    & out   & in \\
		performance &       &       &       &       &       &       & out   & out \\
		total weight &       & in    &       &       &       &       & out   & out \\
		\bottomrule
		\end{tabular}
	  \label{t:ins and outs}
	\end{table}

	In this example, the MCG $M$ is formed in four steps:
	\begin{enumerate}
	\item An analysis block is created for each analysis code using the information in each column of Table \ref{t:ins and outs}. 
	Each analysis block is formed by first creating variable nodes for each input and adding directed edges into a single function node. An edge is directed from this function node into a second function node, which is then directed into variable nodes corresponding to each output. 
	A sample analysis block is shown for analysis code FLOPSa in Fig.~\ref{f:FLOPSb analysis block}.
	\begin{figure}[htb!]
	  \begin{center}
		\includegraphics[width=2.75in]{images/FLOPSa_analysis_block}
	  \end{center}
	  \caption{Sample analysis block for analysis code FLOPSa using Table \ref{t:ins and outs}}
	\label{f:FLOPSb analysis block}
	\end{figure}

@@

	\item A variable nodes is created to represent the geometry variable as a input. Any inputs incorrectly omitted will be identified in step (D).

	\item Connection edges are created that connect each variable node to every other variable node representing variables with the same name. 
	The direction is determined by whether the variable node has an edge directed into or out of a function node, i.e. whether it is a local input or a local output.
	\end{enumerate}
	The resulting MCG is shown in Fig.~\ref{f:MCG holes}. 
	Cycles are shown as dashed lines. FPGs formed from this MCG may or may not retain these cycles.
	\begin{figure}[htb!]
	  \begin{center}
		\includegraphics[width=6in]{images/MCG_edit_holes}
	  \end{center}
	  \caption{Maximal connectivity graph for the subsonic transport example problem}
	\label{f:MCG holes}
	\end{figure}

@@

%	As described in Sec.~\ref{ss:process}, the process of obtaining an FPG from the given MCG is expected to be an iterative process in which the user applies the algorithm to determine whether or not an FPG can be obtained, 
%	and then modifies the indegree limits or the MCG to obtain a satisfactory FPG.
%	For example, after determining the location of a hole, the user can change the indegree limit to make the node a design variable, or the user could change the MCG by adding a new analysis code such that the hole is resolved.
%
%	As presented in Sec.~\ref{s:building graphs}.\ref{ss:obtaining FPG}, the first step to obtaining an FPG is to detect holes. 
%	To begin, we set the lower indegree limit for every node to be unity.

Step (D) now procededs by executing the FPG algorithm. An FPG cannot be obtained because the variable nodes representing the number of engines are holes for NPSS, FLOPSa, and FLOPSb, and the variable nodes representing the mission definition are holes for FLOPSa and FLOPSb. These holes propagated upstream and created holes in the objectives, thereby preventing a valid FPG.

Step (D)(a) begins to resolve this conflict by creating a input for the number of engines. In this example, the number of engines was not originally included as a input to demonstrate how the process responds to this error.
Step (D)(b) then reduces the lower and upper indegree limits for the variable node representing the mission definition to zero, implying that these nodes must be specified as design variables (see Table \ref{t:variable node classification}). The new MCG is shown in Fig.~\ref{f:MCG}.
	\begin{figure}[htb!]
	  \begin{center}
		\includegraphics[width=6in]{images/MCG_edit}
	  \end{center}
	  \caption{The updated MCG with a new input.}
	\label{f:MCG}
	\end{figure}

	Although an FPG may now be obtained, this process has not provided a method to decide which edges to retain when resolving a collision, and these decisions will likely determine which analysis tools are included in the FPG. These decisions are left to the discretion of the designer in the context of the specific implementation. 
	However, the graph-based approach presented in this paper enables standard graph algorithms to be employed to automate these decisions based on considerations of metrics related to the graph or other data related to the analysis. 
	An example is a metric to obtain an FPG with the fewest possible number of cycles. 
In this example, the FPG with the fewest number cycles is shown in Fig.~\ref{f:FPG fewest cycles}, in which the edges belonging to a cycle are inticated by dashed lines. 
For this example problem, the cycles were detected using the implementation of Johnson's algorithm \cite{Johnson1975} in the Python package NetworkX. 
There are two cycles which arise from each local output from PDCYL being directed into FLOPSa and then back into PDCYL.

	Similar alternatives would be to minimize the number of analysis blocks involved in cycles, counting multiplicity, or to minimize the length of the longest cycle (called the \emph{circumference} of the graph). It is beyond the scope of this work to explore efficient methods for finding the FPGs meeting these criteria. However, as discussed by Gabow\cite{Gabow1985}, graph algorithms typically scale well with the size of the graph. This suggests that the computation cost of finding an FPG should be small.
	\begin{figure}[htb!]
	  \begin{center}
		\includegraphics[width=4.5in]{images/FPG_edit_fewest_cycles}
	  \end{center}
	  \caption{FPG with the fewest number of cycles.}
	\label{f:FPG fewest cycles}
	\end{figure}

	Alternatively, it may be desirable to resolve collisions by choosing the higher fidelity analysis tools.
	One method to ensure that the edges directed from certain analysis blocks are those chosen to resolve conflicts is to use a ranking system. Each analysis block is assigned a value by the designer describing how desireable it is for this block to be present in the FPG. The connection edges directed out of each analysis block are then given a weight equal to the value assigned to the analysis block. Finally, each collision is resolved by selected the edges with the highest weights.
For the current example problem, consider the rankings for each analysis code given in Table \ref{t:rankings}.
	\begin{table}[htbp]
	  \centering
	  \caption{Example ranking of importance}
		\begin{tabular}{cc}
		\toprule
		analysis code & rank \\
		\midrule
		VSP   & 5 \\
		PDCYL & 5 \\
		NPSS  & 4 \\
		PMARC & 4 \\
		FLOPSb & 4 \\
		VORLAX & 3 \\
		WATE  & 3 \\
		FLOPSa & 2 \\
		\bottomrule
		\end{tabular}%
	  \label{t:rankings}%
	\end{table}%
	The resulting FPG has four cycles and is shown in Fig.~\ref{f:FPG highest rank}. 
%This graph has four cycles, which are enumerated in Table \ref{t:cycles}.
	\begin{figure}[htb!]
	  \begin{center}
		\includegraphics[width=6in]{images/FPG_edit_ranking}
	  \end{center}
	  \caption{FPG obtained using the ranking system.}
	\label{f:FPG highest rank}
	\end{figure}
%	\begin{table}[htbp]
%	  \centering
%	  \caption{Cycles for the FPG obtained using ranking}
%		\begin{tabular}{ccccccc}
%		\toprule
%		output/input & analysis code & output/input & analysis code & output/input & analysis code & output/input \\
%		\midrule
%		engine weight & FLOPSb & drag  & NPSS  & engine performance & WATE  & engine weight \\
%		engine performance & FLOPSb & drag  & NPSS  & engine performance &       &  \\
%		fuselage weight & FLOPSb & total weight & PDCYL & fuselage weight &       &  \\
%		wing weight & FLOBSb & total weight & PDCYL & wing weight &       &  \\
%		\bottomrule
%		\end{tabular}%
%	  \label{t:cycles}
%	\end{table}%

	Finally, consider a case in which 
the inviscid drag input into FLOPSb is a multi-fidelity input, meaning that 
 multiple analysis codes calculate the same variable. 
	This multi-fidelity formulation is implemented by setting the upper indegree limit for this node as two and then repreating the (automated) process. 
	In this case, both VORLAX and PMARC are retained, resulting in an FPG that omits only FLOPSa.

>>>>

\section{Example Problem}
	\label{s:example problem}
	This section presents an example problem to demonstrate the process of obtaining the FPG and the advantages of doing so. 
The example task is to create an FPG for the conceptual sizing of a single-aisle subsonic transport aircraft using a set of analysis tools with objectives including performance and gross weight for a required mission. 
	The full set of analysis codes available for use is provided in Table \ref{t:analysis codes}.
	\begin{table}[htbp]
	  \centering
	  \caption{Analysis tools for subsonic transport sizing}
		\begin{tabular}{cc}
		\toprule
		analysis tool & description \\
		\midrule
		VSP   & parametric vehicle geometry \\
		PDCYL & wing and fuselage weight estimation \\
		NPSS  & engine sizing and performance \\
		VORLAX & vortex lattice method  aerodynamics \\
		PMARC & low-order panel method  aerodynamics \\
		WATE  & engine weight estimation \\
		FLOPSa & mission performance \\
		  & engine sizing and weight estimation \\
		FLOPSb & mission performance only \\
		\bottomrule
		\end{tabular}%
	  \label{t:analysis codes}%
	\end{table}%
	Each analysis tool contributes individual disciplinary analysis capability, but the outputs of the tools are not mutually exclusive. 
	For example, VORLAX and PMARC are both aerodynamics codes that predict induced drag but with different levels of fidelity. 
	The Flight Optimization System (FLOPS) is included twice to represent two different configurations corresponding to different uses. 
	FLOPSa denotes FLOPS implemented to execute both mission performance and engine analysis, while FLOPSb indicates  FLOPS implemented to execute only mission performance analysis. 
	This representation is useful for ``supercodes'' that are capable of being implemented in different ways and with different sets of inputs and outputs.
The enumeration of these analysis tools and objectives concludes step (A) in Sec.~\ref{ss:process}.

Step (B) is the production of the MCG.
	In this example, the MCG is formed by using a consistant variable naming convention and then connecting all variables with the same name with connection edges. 
	Table \ref{t:ins and outs} presents the full list of variables in the leftmost column and indicates whether the variable is an input or an output of each analysis tool. 
	Some variables, such as geometry and performance, represent groups of variables that are passed as arrays or other data structures due to their similarity. 
	This bundling of variables is not fundamental and does not limit the generality of this example; rather, it simplifies the presentation.
	\begin{table*}[htb!]
	  \centering
	  \caption{Analysis code input and output description}
		\begin{tabular}{ccccccccc}
		\toprule
		variable & \multicolumn{8}{c}{analysis code} \\
		\midrule
			  & VSP   & PDCYL & NPSS  & VORLAX & PMARC & WATE  & FLOPSa & FLOPSb \\
		geometry & in    & in    &       & in    & in    & in    & in    & in \\
		number of engines &       &       & in    &       &       &       & in    & in \\
		mission &       &       &       &       &       &       & in    & in \\
		fuselage weight &       & out   &       &       &       &       & in    & in \\
		wing weight &       & out   &       &       &       &       & in    & in \\
		engine weight &       &       &       &       &       & out   & out   & in \\
		wetted area & out   &       &       &       &       &       & in    & in \\
		inviscid drag &       &       &       & out   & out   &       &       & in \\
		drag  &       &       & in    &       &       &       & out   & out \\
		engine performance &       &       & out   &       &       & in    & out   & in \\
		performance &       &       &       &       &       &       & out   & out \\
		total weight &       & in    &       &       &       &       & out   & out \\
		\bottomrule
		\end{tabular}
	  \label{t:ins and outs}
	\end{table*}

	In this example, the MCG $M$ is formed in four steps:
	\begin{enumerate}
	\item An analysis block is created for each analysis code using the information in each column of Table \ref{t:ins and outs}. 
	Each analysis block is formed by first creating variable nodes for each input and adding directed edges into a single function node. 
A function edge is created from this function node into a second function node, which is then directed into variable nodes corresponding to each output. 
	A sample analysis block is shown for analysis code FLOPSa in Fig.~\ref{f:FLOPSb analysis block}.
	\begin{figure}[htb!]
	  \begin{center}
		\includegraphics[width=3.25in]{images/FLOPSa_analysis_block}
	  \end{center}
	  \caption{Sample analysis block for analysis code FLOPSa using Table \ref{t:ins and outs}}
	\label{f:FLOPSb analysis block}
	\end{figure}

@@

	\item A variable node is created to represent the geometry variable as a input. Any inputs incorrectly omitted will be identified in step (D).

	\item Connection edges are created that connect each variable node to every other variable node representing variables with the same name. 
	The direction is determined by whether the variable node has an edge directed into or out of a function node, i.e. whether it is a local input or a local output.
	\end{enumerate}
	The resulting MCG is shown in Fig.~\ref{f:MCG holes}. 
	Cycles are shown as dashed lines. FPGs formed from this MCG may or may not retain these cycles,  depending on user choices.
	\begin{figure*}[htb!]
	  \begin{center}
		\includegraphics[width=6in]{images/MCG_edit_holes}
	  \end{center}
	  \caption{Maximal connectivity graph for the subsonic transport example problem}
	\label{f:MCG holes}
	\end{figure*}

@@

Step (D) now procededs by executing the FPG algorithm. 
An FPG cannot be obtained because the variable nodes representing the number of engines are holes for NPSS, FLOPSa, and FLOPSb, and the variable nodes representing the mission definition are holes for FLOPSa and FLOPSb. 
These holes are propagated upstream by the FPG algorithm and create holes in the objectives, thereby preventing a valid FPG.

Step (D)(a) begins to resolve this conflict by creating an input for the number of engines. 
In this example, the number of engines was not originally included as an input to demonstrate how the process can reveal the need to select a variable as an input.
Step (D)(b) then reduces the lower and upper indegree limits for the variable node representing the mission definition to zero, implying that these nodes must be specified as design variables (see Table \ref{t:variable node classification}). 
The new MCG is shown in Fig.~\ref{f:MCG}.
	\begin{figure*}[htb!]
	  \begin{center}
		\includegraphics[width=6in]{images/MCG_edit}
	  \end{center}
	  \caption{The updated MCG with a new input.}
	\label{f:MCG}
	\end{figure*}

	Although an FPG may now be obtained, this process has not provided a method to decide which edges to retain when resolving a collision, and these decisions will likely determine which analysis tools are included in the FPG. These decisions are left to the discretion of the designer in the context of the specific implementation. 
	However, the graph-based approach presented in this paper enables standard graph algorithms to be employed to automate these decisions based on considerations of metrics related to the graph or other data related to the analysis. 
	An example is a metric to obtain an FPG with the fewest possible number of cycles. 
In this example, the FPG with the fewest cycles is shown in Fig.~\ref{f:FPG fewest cycles}, in which the edges belonging to a cycle are inticated by dashed lines. 
For this example problem, the cycles were detected using the implementation of Johnson's algorithm \cite{Johnson1975} in the Python package NetworkX. 
There are two cycles which arise from each local output from PDCYL being directed into FLOPSa and then back into PDCYL.

	Similar alternatives would be to minimize the number of analysis blocks involved in cycles, counting multiplicity, or to minimize the length of the longest cycle (called the \emph{circumference} of the graph). It is beyond the scope of this work to explore efficient methods for finding the FPGs meeting these criteria. However, as discussed by Gabow \cite{Gabow1985}, graph algorithms typically scale well with the size of the graph. This suggests that the computation cost of finding an FPG should be small even for large problems.
	\begin{figure*}[htb!]
	  \begin{center}
		\includegraphics[width=4.5in]{images/FPG_edit_fewest_cycles}
	  \end{center}
	  \caption{FPG with the fewest number of cycles.}
	\label{f:FPG fewest cycles}
	\end{figure*}

	Alternatively, it may be desirable to resolve collisions by preferentially choosing analysis tools with favorable properties, such as higher accuracy or minimal run time, whenever possible.
	One method to implement an FPG in this paradigm is to use a ranking system. Each analysis block is assigned a value by the designer describing how desireable it is for this block to be present in the FPG. The connection edges directed out of each analysis block are then assigned a weight equal to the value assigned to the analysis block. Finally, each collision is resolved by selecting the edges with the highest weights.
For the current example problem, consider the rankings for each analysis code given in Table \ref{t:rankings}.
	\begin{table}[htbp]
	  \centering
	  \caption{Example ranking of importance}
		\begin{tabular}{cc}
		\toprule
		analysis code & rank \\
		\midrule
		VSP   & 5 \\
		PDCYL & 5 \\
		NPSS  & 4 \\
		PMARC & 4 \\
		FLOPSb & 4 \\
		VORLAX & 3 \\
		WATE  & 3 \\
		FLOPSa & 2 \\
		\bottomrule
		\end{tabular}%
	  \label{t:rankings}%
	\end{table}%
	The resulting FPG has four cycles and is shown in Fig.~\ref{f:FPG highest rank}. 
	\begin{figure*}[htb!]
	  \begin{center}
		\includegraphics[width=6in]{images/FPG_edit_ranking}
	  \end{center}
	  \caption{FPG obtained using a ranking system.}
	\label{f:FPG highest rank}
	\end{figure*}

	Finally, consider a case in which 
the induced drag input into FLOPSb is a multi-fidelity input, meaning that 
 multiple analysis codes calculate the same variable. 
	This multi-fidelity formulation is implemented by setting the upper indegree limit for this node as two and then repreating the (automated) process. 
	In this case, both VORLAX and PMARC are retained, resulting in an FPG that omits only FLOPSa.
